Project : EXPLORE AND SUMMARISE DATA
========================================================
Name : ELDHOSE PETER
======================================================
<b>This tidy data set contains 1,599 red wines with 11 variables on the chemical \
properties of the wine. At least 3 wine experts rated the quality of each wine, \
providing a rating between 0 (very bad) and 10 (very excellent). 

Dataset: RED WINE QUALITY
================================

Link To Dataset :
====================================================================
https://www.google.com/url?q=https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityReds.csv&sa=D&ust=1501101448933000&usg=AFQjCNE5OzgFN193HQmVR-J8tNpYavMvcA



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(reshape2)
library(gridExtra)
library(GGally)
```

Loading the data set
========================================================================

```{r  Load_the_Data}
df<-read.csv('wineQualityReds.csv')
data_new <-subset(df,select=-c(X))

```


About the dataset
=============================================================================
The dataset consist of 1599 observations of 13 variables. \
Variable 'X' is the id given for each observation. \
At least 3 wine experts rated the quality of each wine, providing a rating \
between 0 (very bad) and 10 (very excellent). \
Except 'X' and 'quality', all other variables are of datatype 'numeric'. <br> 
'X' and quality are of 'integer' datatype. 


<b>Attribute information:</b>
==================================

   Input variables (based on physicochemical tests):<br>
   1 - fixed acidity (tartaric acid - g / dm^3)<br>
   2 - volatile acidity (acetic acid - g / dm^3)<br>
   3 - citric acid (g / dm^3)<br>
   4 - residual sugar (g / dm^3)<br>
   5 - chlorides (sodium chloride - g / dm^3)<br>
   6 - free sulfur dioxide (mg / dm^3)<br>
   7 - total sulfur dioxide (mg / dm^3)<br>
   8 - density (g / cm^3)<br>
   9 - pH<br>
   10 - sulphates (potassium sulphate - g / dm^3)<br>
   11 - alcohol (% by volume)<br>
   Output variable (based on sensory data):<br>
   12 - quality (score between 0 and 10)<br>
  Quality score ranges between 0(being very bad) and 10(being very excellent)<br>
   
   Description of attributes: \

   1 - fixed acidity: most acids involved with wine or fixed or <br> 
   nonvolatile (do not evaporate readily). \

   2 - volatile acidity: the amount of acetic acid in wine, which at too \
   high of levels can lead to an unpleasant, vinegar taste. \

   3 - citric acid: found in small quantities, citric acid can \
   add 'freshness' and flavor to wines. \

   4 - residual sugar: the amount of sugar remaining after fermentation stops, \
   it's rare to find wines with less than 1 gram/liter and wines with greater \
   than 45 grams/liter are considered sweet. \

   5 - chlorides: the amount of salt in the wine. \

   6 - free sulfur dioxide: the free form of SO2 exists in equilibrium between <br> 
   molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial \
   growth and the oxidation of wine. \

   7 - total sulfur dioxide: amount of free and bound forms of S02; in low <br> 
   concentrations, SO2 is mostly undetectable  in  wine,   but at free SO2 \
   concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine. \

   8 - density: the density of water is close to that of water depending on \
   the percent alcohol and sugar content. \

   9 - pH: describes how acidic or basic a wine is on  a  scale  from  0 <br> 
   (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale. \

   10 - sulphates: a wine additive which can contribute to sulfur dioxide <br> 
   gas (S02) levels, wich acts as an antimicrobial and antioxidant. \

   11 - alcohol: the percent alcohol content of the wine. \

   Output variable (based on sensory data): <br> 
   12 - quality (score between 0 and 10) \
   
Reference : https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt


Structure of the dataset
======================================================

```{r echo=FALSE}
str(df)
```



# Univariate Plots Section

Lets plot all the variables in data set. This will provide information regarding <br>
the distribution of various chemical properties in the red wine. \

```{r , fig.width=15,fig.height=15,echo=FALSE, Univariate_Plots, warning=FALSE, message=FALSE}

#Lets modify data set with new names.

data_<-rename(data_new,fixed.acidity_g.per.dm3 = fixed.acidity,
      volatile.acidity_g.per.dm3 = volatile.acidity,citric.acid_g.per.dm3=citric.acid,
      residual.sugar_g.per.dm3 = residual.sugar,chlorides_g.per.dm3=chlorides,
      free.sulfur.dioxide_mg.per.dm3 = free.sulfur.dioxide,
      total.sulfur.dioxide_mg.per.dm3 = total.sulfur.dioxide,
      density_g.per.cm3=density,sulphates_g.per.dm3 = sulphates,
      alcohol_percentagebyvolume = alcohol)


melt_data<-melt(data_)
qplot(value, data=melt_data,bins = 50,color='Red') +
  facet_wrap(~variable,scales ='free',drop = FALSE,nrow=4) 
```


The above graphs shows distribution of various variables in the data set. \
Volatile acidity, density and pH appeared to be normally distributed.Some of the <br> distributions like residual sugar and chlorides are long tailed. \
To get better understanding of long tailed distribution, we can use log 10 \
transformations. \


###Lets transform the x axis of the long tailed plots using log 10.


```{r echo=FALSE}
ggplot(data=data_,aes(x=residual.sugar_g.per.dm3))+
  geom_histogram(bins=70,color='Black')+
  scale_x_log10()+xlab('log10(residual.sugar(g/dm^3))')
ggplot(data=data_,aes(x=chlorides_g.per.dm3))+
  geom_histogram(binwidth=0.01,color='Blue')+
  scale_x_log10()+xlab('log10(chlorides(g/dm^3))')
```

The log 10 transformation tranforms the residual sugar and chlorides plots <br> 
roughly to normal distributions.<br> 



Univariate Analysis
======================================

###Summary of the dataset

```{r echo=FALSE,summary}

summary(data_new)

```

```{r echo=FALSE, occurences}
# Lets see the occurences of different quality levels in data set.
tb<-table(data_new$quality)

```



Occurences of different quality levels in dataset:<br>
Quality:Count<br>
3: 10<br>
4: 53<br>
5:681<br>
6:638<br>
7:199<br>
8:18<br>

### What is the structure of your dataset?

The dataset consist of 1599 observations of 13 variables("X","fixed.acidity" <br>  ,"volatile.acidity", "citric.acid","residual.sugar","free.sulfur.dioxide", \
"chlorides","total.sulfur.dioxide", "density","pH","sulphates","alcohol", \
"quality").<br>
Variable 'X' is the id given for each observation. \
Quality : Rated the quality of each wine, providing a rating between 0(very bad) \
and 10 (very excellent).<br>
Except 'X' and 'quality', all other variables are of datatype 'numeric'. 'X' and \
quality are of 'integer' datatype.<br>

From the histograms plotted, we can see that the red wine quality 5 and 6 have \
most occurences in the data set.<br>

Volatile acidity, density and pH appeared to be normally distributed.Some of <br> 
the distributions are long tailed. Some of the distributions  like residual \
sugar and chlorides are long tailed. \

The fixed acidity varies from 4 to 16 (g/dm^3) with mean value of 8.32.The \
volatile acidity varies from  0.1 to 2(g/dm^3)  with a mean of 0.527.The \
citric acid varies from  0 to 1(g/dm^3)  with a mean of 0.271.The residual <br> 
sugar varies from  0.9 to 15(g/dm^3)  with a mean of 2.539.The chlorides \
varies from  0.01 to 7(g/dm^3)  with a mean of 0.087.The free.sulfur.dioxide <br> 
varies from 1 to 72(mg/dm^3)   with a mean of 15.87. The total.sulfur.dioxide \
varies from 6 to 289(mg/dm^3)   with a mean of 46.47. The density  varies  \
from 0.9 to 2(g/cm^3)  with a mean of 0.996.The  pH  varies from  2 to 5  \
with a mean of 3.311.The  sulphates  varies from  0.3 to 2(g/dm^3)  with a <br> 
mean of 0.6581. The alcohol varies from  8 to 15(%/volume)  with a mean of \
10.42. The quality varies from  3 to 8  with a mean of 5.636. \


Questions
========================================
<h3> What is/are the main feature(s) of interest in your dataset?<br></h3>
The main objective of the study is quality of the red wine based on various \
factors.<br> 

<h3>What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?<br></h3>
The acidity is indicated by pH level. So pH will be considered as an important <br> 
aspect of dataset. \

<h3>Did you create any new variables from existing variables in the dataset?<br></h3>
I did not create new variable from the existing variables in the dataset. \
I created another data by using melt function inorder to plot the histograms <br> 
of various variables. \

<h3> Of the features you investigated, were there any unusual distributions?  <br></h3>
Residual sugar and chlorides had a long tail distribution. So I scaled the x \
axis using log 10.Also, the quality in the dataset varies from 3 to 8. \




# Bivariate Plots Section


Lets plot quality of the red wine against all other chemical properties to find \
which chemical properties  affects the quality of red wine.I have choosen \
box plot as they can represent categorical data such as quality in a better way.\

 
```{r echo=FALSE, Bivariate_Plots}


mul<-function(data=data_new,var,xl,yl){
  
ggplot(data=data,aes(x=factor(quality),y= var)) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+xlab(xl)+ylab(yl)+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)

}


mul(df,var<-data_new$alcohol,'quality','alcohol(%/volume)')
mul(data_new,var<-data_new$fixed.acidity,'quality','fixed.acidity(g/dm^3)')
mul(data_new,var<-data_new$volatile.acidity ,'quality','volatile.acidity(g/dm^3)')
mul(data_new,var<-data_new$residual.sugar ,'quality','residual.sugar(g/dm^3)')
mul(data_new,var<-data_new$citric.acid ,'quality','citric.acid(g/dm^3)')
mul(data_new,var<-data_new$chlorides  ,'quality','chlorides(g/dm^3)')
mul(data_new,var<-data_new$free.sulfur.dioxide,'quality','free.sulfur.dioxide(mg/dm^3)')
mul(data_new,var<-data_new$total.sulfur.dioxide,'quality','total.sulfur.dioxide(mg/dm^3)')
mul(data_new,var<-data_new$density,'quality','density(g/cm^3)')
mul(data_new,var<-data_new$pH ,'quality','pH(g/dm^3)')
mul(data_new,var<-data_new$sulphates ,'quality','sulphates(g/dm^3)')

```


The above graphs provided insights to the red wine data set.We can see that some \
distributions have higher number of outliers like residual sugar and  chlorides <br> 
as we saw earlier.From the box plots too, we can see that most of the samples of \
red wine in the data set have a quality of 5 and 6.We can clearly see that, with \
the increase of alcohol content  in red wine, it tends to show better quality. \
Similarly, with the decrease in volatile acidity,quality tends to be better. \
The box plots also provided information regarding range of values,the median, \
the mean values of different chemical properties corresponding to different \
quality levels.

Lets analyze this further using correlation plot.This will give us a better  \
understanding of data and lets see which variables have stronger relationships \
with quality of red wine. \



###Correlation Plot

```{r echo=FALSE,fig.width=10,fig.height=8,}
ggcorr(data_new,geom='circle', hjust = 0.75,size=3,nbreaks = 5,layout.exp = 1)+
theme_dark()
```

The above graph shows correlations among different variables in the data set. \
The correlation plot shows correlations among different variables in the data \
set.Stronger correlations, darker the color. 

```{r echo=FALSE}
#Lets find top correlations.
a<-cor(data_new,method='pearson')
b<-subset(a,select=quality)
c<-melt(b)
d<-arrange(c,desc(abs(value)))

```



Variables which were found to exhibit good correlation with quality are:
======================================================================

alcohol : 0.476<br>
volatile acidity : -0.390<br>
sulphates : 0.251<br>
citric acid : 0.226<br>

# Bivariate Analysis

After investigating the data set, mainly four varibales were found to exhibit <br> 
good correlation with quality.They include alcohol,volatile acidity, sulphates \
and citric acid. \
Alcohol content has the highest correlation with the red wine quality. The \
graph below shows the relationship between the quality and alcohol content. \
We have choosen alpha =1/4 and jiter to reduce overplotting. \


```{r echo=FALSE}
ggplot(data=data_new,aes(quality,y=alcohol,title=('alcohol vs quality')))+
  geom_jitter(alpha=1/4,color=('Red'))+
  ylab('alcohol(%/volume)')
```


<b>The volatile acidity is negatively correlated with the quality.</b>


```{r echo=FALSE}
ggplot(data=data_new,aes(quality,y=volatile.acidity,
                         title=('volatile acidity vs quality')))+
  geom_point(alpha=1/4,color=('Blue'),position = 'jitter')+
  ylab('volatile.acidity(g/dm^3)')

```


From the graphs we can see an approximate linear relationship between few <br> 
variables and quality of the red wine.Alcohol and volatile acidity should be \
noted as they showed good linear relationship with quality. \
<b>The graphs  clearly shows the factors affecting the quality of the red wine.<br></b>
Good quality red wine tends to have:<br>
Higer alcohol content.<br>
Lower volatile acidity.<br>
Good amount of sulphates and citric acid.<br>



```{r echo=FALSE}
#Lets find top variables exhibiting correlation other than the quality.So we 
#subset the data set without including the quality.

s<-subset(cor(data_new),select=-quality)
a1<-head(arrange(melt(subset(s,select=fixed.acidity)),desc(abs(value))),3)
a2<-head(arrange(melt(subset(s,select=pH)),desc(abs(value))),3)
a3<-head(arrange(melt(subset(s,select=citric.acid)),desc(abs(value))),3)
a4<-head(arrange(melt(subset(s,select=density)),desc(abs(value))),3)
a5<-head(arrange(melt(subset(s,select=volatile.acidity)),desc(abs(value))),3)
a6<-head(arrange(melt(subset(s,select=sulphates)),desc(abs(value))),3)
a7<-head(arrange(melt(subset(s,select=free.sulfur.dioxide)),desc(abs(value))),3)
a8<-head(arrange(melt(subset(s,select=residual.sugar)),desc(abs(value))),3)
a9<-head(arrange(melt(subset(s,select=total.sulfur.dioxide)),desc(abs(value))),3)
a10<-head(arrange(melt(subset(s,select=chlorides)),desc(abs(value))),3)
a11<-head(arrange(melt(subset(s,select=alcohol)),desc(abs(value))),3)

```

 <b><h3>We can see good correlation with some other variables :</h3><br>
 
 fixed acidity and pH : -0.683<br>
 fixed acidity and citric acid : 0.672<br>
 fixed acidity and density : 0.668<br>
 citric acid and Ph : -0.541<br>
 citric acid and volatile acidity : -0.552<br>
alcohol and density : -0.496<br>
</b>


<b><h3>Lets visualize some of these relationships.</h3>

We use alpha = 1/4 to reduce overplotting.

```{r echo =FALSE, warning=FALSE, message=FALSE}
ggplot(data=data_new,aes(pH,y=fixed.acidity,title=('Fixed.acidity vs pH')))+
  geom_point(alpha=1/4,color=('Orange'))+
  geom_smooth(se=FALSE)+ylab('fixed.acidity(g/dm^3)')

ggplot(data=data_new,aes(citric.acid,y=fixed.acidity,
                         title=('citric.acidity vs fixed.acidity'))) +
  geom_point(alpha=1/4,color=('Blue'))+
  geom_smooth(se=FALSE,color='Red')+
  ylab('fixed.acidity(g/dm^3)')

ggplot(data=data_new,aes(density,y=fixed.acidity,title=('Density vs Fixed.acidity')))+
  geom_point(alpha=1/4,color=('Green'))+
  geom_smooth(se=FALSE)+ylab('fixed.acidity(g/dm^3)')

ggplot(data=data_new,aes(alcohol,y=density,title=('Alcohol vs density')))+
  geom_point(alpha=1/4,color=('Violet'))+
  geom_smooth(se=FALSE)+ylab('Density(g/cm^3)')
```
   
   
The above graph clearly shows there exist an approximate linear relationship \
between these chemical properties. \


Median of chemical properties categorized based on quality.
===============================================================================

```{r echo=FALSE}

cal<-function(dfr,var){
  val<-c()
  j<-1
  
  for (i in c(3:8)){
    val[j]<-with(dfr, median(var[quality == i]))
    j<-j+1
  }
  return (val)
  }


```

```{r echo=FALSE}
quality<-c(3:8)
fixed.acidity<-cal(df,df$fixed.acidity)
volatile.acidity<-cal(df,df$volatile.acidity)
citric.acid<-cal(df,df$citric.acid)
residual.sugar<-cal(df,df$residual.sugar)
chlorides<-cal(df,df$chlorides)
free.sulfur.dioxide<-cal(df,df$free.sulfur.dioxide)
total.sulfur.dioxide<-cal(df,df$total.sulfur.dioxide)
density<-cal(df,df$density)
pH<-cal(df,df$pH)
sulphates<-cal(df,df$sulphates)
alcohol<-cal(df,df$alcohol)

median_fr<-data.frame(quality,fixed.acidity,volatile.acidity,citric.acid,
 residual.sugar,chlorides,free.sulfur.dioxide,total.sulfur.dioxide,density,
 pH,sulphates,alcohol)
median_fr
```





# Multivariate Plots Section

Trends of chemical properties and its affect on quality of the red wine.
==============================================================================

Here we plot the variables having high correlation with quality, all together. \
We will also use a coloring mechanism such that low quality wines are plotted \
using light shades while high quality wines are plotted using dark shades. We \
will also plot regression lines to get a deep understanding of variation of \
quality of red wines with these chemical properties. \


```{r , fig.width=10,fig.height=8,echo=FALSE}
ggplot(data=df,aes(alcohol,y=volatile.acidity,color=factor(quality),
                   title=('Alcohol vs Volatile.acidity'))) +
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('alcohol(%/volume)')+ylab('volatile.acidity(g/dm^3)')
```
```{r , fig.width=10,fig.height=8,echo=FALSE}


ggplot(data=df,aes(fixed.acidity,density,color=factor(quality),
                   title=('Fixed.acidity vs Density'))) +
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='Greens',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('fixed.acidity(g/dm^3)')+ylab('density(g/cm^3)')
```

```{r , fig.width=10,fig.height=8,echo=FALSE}


ggplot(data=df,aes(alcohol,density,color=factor(quality),title=('Alcohol vs Density')))+
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='Reds',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('alcohol(%/volume)')+ylab('density(g/cm^3)')
```

```{r, fig.width=10,fig.height=9, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(data=df,aes(volatile.acidity,citric.acid,color=factor(quality),
                   title=('Volatile.acidity vs Citric.acid'))) +
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='BuPu',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('volatile.acidity(g/dm^3)')+ylab('citric.acid(g/dm^3)')+
  scale_y_continuous(limits=c(0,NA))

```

```{r , fig.width=10,fig.height=8,echo=FALSE}


ggplot(data=df,aes(sulphates,citric.acid,color=factor(quality),
                   title=('Sulphates vs Citric.acid'))) +
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='RdPu',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('sulphates(g/dm^3)')+ylab('citric.acid(g/cm^3)')
```


# Multivariate Analysis

We have plotted graphs using the variables alcohol,volatile acidity,density, \
fixed acidity and citric acid against quality of the red wine.In all the graphs, \
it clearly seen that have higher alcohol content and lower volatile acidity \
tends to have better quality. \
In the previous sections, we saw that citric acid and volatile acidity are <br> 
negatively correlated.This is very mch reflected in graphs plotted as it shows \
higher citric acid and lower volatile acidity, better the red wine quality.The \
graphs also shows that lower the density and higer the alcohol, we will have \
better quality of red wine. \






# Final Plots and Summary


## Plot One

The plot represents variation of quality with alcohol and volatile acidity.


```{r echo=FALSE, fig.width=10,fig.height=8,, warning=FALSE, message=FALSE }

ggplot(data=df,aes(alcohol,y=volatile.acidity,color=factor(quality),
                       title=('Alcohol vs Volatile.acidity')))+
  geom_point(alpha=0.8,size=1)+geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',guide=guide_legend(title='Quality'))+
  theme_dark()+
  xlab('alcohol(%/volume)')+ylab('volatile.acidity(g/dm^3)')

```


### Description One

The graphs show that lower volatile acidity and higher alcohol content tends to \
show better quality.Volatile acidity is negatively correlated . The lighter \
regression line represents the low quality wines while darker line represents \
high quality wines. 
Stronger correlations, darker the color. 
The red wine quality is highly correlated with the variables alcohol,volatile <br> acidity,sulphates and citric acid.Red Wines with high alcohol content tends to \
show better quality. They show good correlation with the quality of red wine.<br>
alcohol : 0.476<br>
volatile acidity : -0.390<br>
sulphates : 0.251<br>
citric acid : 0.226<br>

## Plot Two

The plot represents variation of quality with volatile acidity and citric acid. \


```{r, fig.width=10,fig.height=9, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(data=df,aes(volatile.acidity,citric.acid,color=factor(quality),
                   title=('Volatile.acidity vs Citric.acid'))) +
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='BuPu',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('volatile.acidity(g/dm^3)')+ylab('citric.acid(g/dm^3)')+
  scale_y_continuous(limits=c(0,NA))

```



### Description Two


The graph shows that the volatile acidity and citric acid  are  negatively  \
correlated. Dark regression lines represent high quality wines while light \
regression lines represent low quality wines. Low concentration of volatile acid \
and high concentration of citric acid tends to show better quality of red wines. \


## Plot Three


The plot represents variation of quality with sulphates and citric acid.

```{r echo=FALSE,fig.width=10,fig.height=8, Plot_Three}
ggplot(data=df,aes(sulphates,citric.acid,color=factor(quality),
                   title=('Sulphates vs Citric.acid')))+
  geom_point(alpha=0.8,size=1)+
  geom_smooth(method='lm',se=FALSE,size=1)+
  scale_color_brewer(type = 'seq',palette='RdPu',guide=guide_legend(title='Quality'))+
  theme_dark()+

  xlab('sulphates(g/dm^3)')+ylab('citric.acid(g/cm^3)')
```

### Description Three

The graph shows that higher citric acid and sulphate  is associated with high \
quality wine.The dark regression lines represent high quality wines while  \
light regression lines represent low quality wines.

# Reflection

From the univariate plots, I was able to know about the distribution of various \
chemical properties in the data set. 

Some of the distributions were long tailed. So logarithmic transformations <br> 
were used to reduce the effects of outliers.Residual sugar and chlorides had a \
long tailed distribution.Some of the graphs were overplotted, so I adjusted the \
alpha level and figure size. \

In bivariate plots,I have used box plots and sctter plots and it have provided \
me a great insight to the chemical properties which significantly contributes \
to the red wine quality. \
The multivarite variate plots have shown which pair of chemical properties tends \
to give better quality of red wine. 

One of the things which I noted was that the number of samples of wines with <br> 
quality 5 and 6 was significantly higher than others.The study can be improved \
with greater number of samples. \

One of the things I noted was that many samples of red wine had 0 quantity of \
citric acid.

We have found correlation between many variables in the dataset. \
The quality of red wines were highly correlated with alcohol,volatile acidity, \
citric acid and sulphates.The higher alcohol content tends to give better \
quality of wine.The volatile acidity was another variable which was affecting <br> 
the wine quality negatively.Lower content of volatile acid and higher content \
of citric acid were shown to give better quality of wine. \
Higher content of sulphates were also seen to be associated with high quality <br> 
of wine.To summarise, higher content of alcohol,citric acid,sulphates and \
lower volatile acidity tends to give better quality of wine. \
We can see good correlation with some other variables like fixed acidity and pH, \
fixed acidity and citric acid,fixed acidity and density, citric acid and \
volatile acidity.


Even though there shows significant correlation between quality and other \
variables, correlation does not mean causation.We cannot say that higher alcohol \
content gives better quality of wine.We can only conclude that there is \
considerable amount of alcohol in red wines having higher quality. \


Future improvement can be done by increasing the number of red wine samples. \
Here in this data set, the occurences of wines of quality 5 and 6 are \
significantly higher than that of the wines of other qualities.The data must \
collected for very low quality wines and very high quality wines. In this \
data set, samples of wines having quality 3,4 and 8 are very low.



